Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-03 paper/ms.tex
Update fractional errors for one orbit

Figure~\ref{fig:one_orbit_wrong_ref} shows that the erroneous observer would
infer significant time evolution in their computed actions. The
95\textsuperscript{th} minus 5\textsuperscript{th} percentiles are $8.7$,
$47.1$, and $19.3\,\actunit$ for $J_r$, $L_z$, and $J_z$, respectively. These
are fractional errors of $26.5\%$, $3.1\%$, and $81.4\%$, respectively.

>>>>

Figure~\ref{fig:one_orbit_wrong_ref} shows that the erroneous observer would
infer significant time evolution in their computed actions. The
95\textsuperscript{th} minus 5\textsuperscript{th} percentiles are $2.2$ and
$6.2 \actunit$ for $J_r$ and $J_z$, respectively. These are fractional errors
of $5.7\%$ and $85.7\%$, respectively. The error induced in $L_z$ is
negligible, as expected since $L_z$ does not depend on the value of $z$. It is
worth pointing out that a $100\,\pc$ error in an orbit with
$z_{\text{max}}=425\,\pc$ --- a $24\%$ error --- induced an $85.7\%$ error in
the computation of $J_z$.
